K Nearest Neighbour Search Using Space-filling Curves

### 2013-12-07 paper/paper.tex
added the graphs to the paper

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{YeaGra.png}
\caption{The Runtime Analysis of the Yeast Database.}
\label{run-yeast}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{ArcGra.png}
\caption{The Runtime Analysis of the Acrene Database.}
\label{run-arcene}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{LatGra.png}
\caption{The Runtime Analysis of the Lattice Database.}
\label{run-lattice}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{YeaGra2.png}
\caption{The Approximation bound of the Yeast Database.}
\label{approx-yeast}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{ArcGra2.png}
\caption{The Approximation bound of the Acrene Database.}
\label{approx-acrene}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{LatGra2.png}
\caption{The Approximation bound of the Lattice Database.}
\label{approx-lattice}
\end{center}
\end{figure}
